Non-standard evaluation inside functions and loops

### 2023-04-04 text/23/non-standard-evaluation.Rmd
Added an extra note to non-standard-evaluation

@@

But `select`, a function in dplyr can do the same work without the quote marks.

>>>>

### A brief warning

The example I show below are simple. It helps me to understand things better by working out simple examples. But the examples are so simple that you might ask yourself why bother with this, or why not try something even simpler. Bear with me, though, because the simple examples illustrate some general principles that will help you in more complex settings.

@@

But `select`, a function in dplyr, can do the same work without the quote marks.
